\documentstyle[hyperref, margin, line]{res}


\hypersetup{backref, %pdfpagemode=none,%FullScreen,
colorlinks=true,backref, urlcolor=blue, %filecolor=blue
}

 \oddsidemargin -.6in
 \evensidemargin -.6in

% \topmargin 2cm
 \addtolength{\topmargin}{-.5in}
 \addtolength{\textheight}{1in}

\textwidth=6.0in \itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\renewcommand{\namefont}{\Huge\textsf}

\begin{document}

\sffamily

 \name{Jithu Sunny \vspace*{.1in}} \hfill April 2012

\begin{resume}


\section{\sc {\bf \textsf{CONTACT INFORMATION}}}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Kalapurakkal House   & {\it Mobile:}  +91 9567 175 660 \\
Madonna Nagar   & {\it Resi:}    +91 4872 357 392   \\
P.O. Ollur & {\it E-mail:}
\href{mailto:jithusunnyk@gmail.com}{\underline{jithusunnyk@gmail.com}}
\\
Thrissur, Kerala  & {\it WWW:}
\href{http://jithusunnyk.blogspot.com}{\underline{http://jithusunnyk.blogspot.com}}
 \\
India
\end{tabular}

\vspace*{+2mm}
\section{\sc {\bf \textsf{BIOGRAPHICAL \qquad DATA}}}
Age: 21\\
Gender: Male\\
Citizenship: India\\
Date and place of birth: 28th September 1990, Thrissur, Kerala \\

\vspace*{+2mm}

\section{\bf \textsf{OBJECTIVE}}
To pursue a career through which I could continue to explore, learn \& put in action the technology for a purpose.

\vspace*{+2mm}

\section{\bf \textsf{EDUCATION}}
{\bf \textsf{Government Engineering College}}, Thrissur, Kerala.\\
\vspace*{-.1in}

\begin{list1}
\item[] B.Tech in Computer Science \& Technology, June 2008 - March 2012(pursuing)  \qquad (72.5\%)\\ University of Calicut 
\end{list1}

{\bf \textsf{Don Bosco HSS}}, Mannuthy, Kerala.\\
\vspace*{-.1in}
\begin{list1}
\item[] Plus-Two, 2006-2008 - Kerala State Higher Secondary Education\qquad \qquad(94.16\%)
\end{list1}

{\bf \textsf{Holy Angel's HS}}, Ollur, Kerala.\\
\vspace*{-.1in}
\begin{list1}
\item[] SSLC, 2005-2006 - Kerala State Board\qquad \qquad \qquad(88\%)
\end{list1}

\vspace*{+3.5mm}
 \section{\sc \bf \textsf{TECHNICAL SKILLS}}
\textbf{Languages \& APIs}
\begin{itemize}
\item \textbf{Proficient:} C, Python, GUI Programming - PyQt4, Microcontroller Programming(In C for AVR family).
\item \textbf{Familiar:} Java, Lisp, BASH scripting, 8086 Assembly language, Prolog, PHP, Javascript, CSS, AJAX, VB.NET.
\end{itemize}

\textbf{Version Control Systems}
\begin{itemize}
\item Git - \href{https://github.com/jithusunny}{\underline{https://github.com/jithusunny}}
\end{itemize}

\textbf{Platforms}
\begin{itemize}
\item GNU/Linux, Microsoft Windows.
\end{itemize}

\textbf{Authoring \& Graphics}
\begin{itemize}
\item \LaTeX\ , \LaTeX\ Beamer, GIMP
\end{itemize}

\vspace*{+2mm} 

\section{\sc \bf \textsf{B.Tech MAIN PROJECT}}
{\bf \textsf{Webtop}}\\
\vspace*{-.1in}

\begin{list1}
\item[] Desktop environment simulated in a web browser that gives the user power to access his desktop from anywhere. \qquad (In progress)
\end{list1}

\vspace*{+3.5mm}

\section{\sc \bf \textsf{B.Tech \qquad SEMINAR}}
{\bf \textsf{Augmented Reality: Technology \& Applications}}\\
\vspace*{-.1in}

\begin{list1}
\item[] The general working of an AR system. Basic computer vision algorithms, hardware technologies and real-world applications of Augmented Reality.
\end{list1}

\vspace*{+3.5mm}

\section{\sc \bf \textsf{B.Tech MINI PROJECT}}
{\bf \textsf{Python controlled General Purpose Vehicle}}\\
\vspace*{-.1in}

\begin{list1}
\item[] In this Embedded Systems project, we created the prototype of a vehicle that can be controlled using a remote computer. Through the GUI developed in PyQt4 the user can control the car. The little intelligence in the vehicle is an Atmel Atmega8 microcontroller which is programmed in C and compiled using gcc-avr cross compiler. RF modules are used for wireless communication.
\\
\item[] \textbf{Source:} \href{https://github.com/jithusunny/Mini-Project}{\underline{https://github.com/jithusunny/Mini-Project}}
\end{list1}

\vspace*{+2mm}

\section{\sc \bf \textsf{AS A SPEAKER}}
February 2010 \textbf{Venue} : FreeZone, Govt. Engineering College, Thrissur. \textbf{Topic} : Stellarium

\vspace*{+2mm}

\section{\sc \bf \textsf{ACHIEVEMENTS, ACTIVITIES \& HOBBIES}}
\begin{itemize}
\item Winner on two consecutive days in \textbf{Mobme Codejam, A 14-day State wide Programming Competition} organized in June 2011 by Mobme Wireless - \href{http://codejam.mobme.in/results}{\underline{http://codejam.mobme.in/results}}
\item First prize in \textbf{Online C-Programming competition} hosted by Vidya Academy of Science and Technology in relation with Perizia 3.0 in April 2011.
\item First Prize in \textbf{Ciphering} \& \textbf{Coding} competitions held at Invento'12 - Govt Engg College, Palakkad in March 2012.

\item Developed \textbf{The Resultmanager} for assisting the teachers to fetch and analyse the results of any batch of students under Calicut University. The program is written in Python. It fetches the result pages of the specified batch and figures out these - the individual total marks and percentage, the class-wise, subject-wise pass percentage \& the class topper.\\
\\ \textbf{Code Repo:} \href{https://github.com/jithusunny/Resultmanager}{\underline{https://github.com/jithusunny/Resultmanager}}

\item Secured second prize in a quiz competition jointly organized by Microsoft \& IEEE at Govt. Engineering college in Jan 2011.
%\item Active \textbf{Free Software Hacktivist} and member of Free Software User's Group(FSUG) Thrissur.
\item Love coding in Python, admire Functional Programming, typeset using \LaTeX\ \& support UNIX philosophy.
\item \textbf{Electronics hobbyist}. Spends time hands on Embedded systems and microcontroller programming.
\item \textbf{Singer}, bagged prizes in several competitions at school level and sub-district level. Appreciate seemingly unmixable genres of music like Classical \& Metal.
\item A \textbf{Tabala} player.
\item In love with \textbf{deep forests} and wild nature.
\item Favorite pastime after Trekking is reading. A budding up fiction writer.
\end{itemize}

\vspace*{+2mm}

\section{\sc \bf \textsf{BLOG}}
I maintain a blog at \href{http://jithusunnyk.blogspot.com}{\underline{http://jithusunnyk.blogspot.com}}.

\section{\sc {\bf \textsf{REFERENCES}}}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Valsaraj K S   &  Helen K J \\
Assistant Professor \& HOD   & Assistant Professor   \\
GEC, TCR   &  GEC, TCR  \\
0487-26809230 & 9446352699 \\
\href{mailto:valsaraj.ks@gmail.com}{\underline{valsaraj.ks@gmail.com}} & 
\href{mailto:helenkj28@gmail.com}{\underline{helenkj28@gmail.com}}
\end{tabular}

\end{resume}
\end{document}
